Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-08-05 Masterarbeit_Robotik_Pamuk.tex
Figure and Table after each Tuning

\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\columnwidth]{img/max_latency_default.png}
	\caption[Latency with default settings]{Latency with default settings}
	\label{fig:max_latency_default}
\end{figure}

@@

After the BIOS configurations,

@@

@@

@@

@@

%
% Hier beginnt der Anhang.
%
\clearpage
\appendix

\chapter{Anhang A}
\clearpage

\chapter{Anhang B}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/max_latency_default.png}
	\caption[Latency with default settings]{Latency with default settings}
	\label{fig:max_latency_default}
\end{figure}

@@

After the BIOS configurations, Figure \ref{fig:max_latency_rt}

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/3rt/max_latency_rt/max_latency_rt.png}
	\caption[After BIOS configurations]{After BIOS configurations}
	\label{fig:max_latency_rt}
\end{figure}

\begin{table}[H]
	\centering
	\caption[Latency statistics of Salamander 4 after BIOS configurations]{Latency statistics of Salamander 4 virtualization after BIOS configurations in microseconds}
	\label{tab:latency_statistics_virt}
	\setlength{\tabcolsep}{0.5em} % for the horizontal padding
	{\renewcommand{\arraystretch}{1.2}% for the vertical padding
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
	Average Latency & 17.68 \\\hline
	Maximum Latency & 32.21 \\\hline
	Minimum Latency & 8.005 \\\hline
	Standard Deviation & 6.1 \\\hline
	\end{tabular}}
	\end{table}

@@

After the Kernel configurations, Figure \ref{fig:max_latency_rt_kernelparam}

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/4rt_kernelparam/max_latency_rt_kernelparam/max_latency_rt_kernelparam.png}
	\caption[After Kernel configurations]{After Kernel configurations}
	\label{fig:max_latency_rt_kernelparam}
\end{figure}

\begin{table}[H]
	\centering
	\caption[Latency statistics of Salamander 4 after Kernel configurations]{Latency statistics of Salamander 4 virtualization after Kernel configurations in microseconds}
	\label{tab:latency_statistics_virt}
	\setlength{\tabcolsep}{0.5em} % for the horizontal padding
	{\renewcommand{\arraystretch}{1.2}% for the vertical padding
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
	Average Latency & 14.00 \\\hline
	Maximum Latency & 21.694 \\\hline
	Minimum Latency & 6.351 \\\hline
	Standard Deviation & 1.44 \\\hline
	\end{tabular}}
	\end{table}

@@

After the Host configurations, Figure \ref{fig:max_latency_rt_kernelparam_host}

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/5rt_kernelparam_host/max_latency_rt_kernelparam_host/max_latency_rt_kernelparam_host.png}
	\caption[After Host configurations]{After Host configurations}
	\label{fig:max_latency_rt_kernelparam_host}
\end{figure}

\begin{table}[H]
	\centering
	\caption[Latency statistics of Salamander 4 after Host configurations]{Latency statistics of Salamander 4 virtualization after Host configurations in microseconds}
	\label{tab:latency_statistics_virt}
	\setlength{\tabcolsep}{0.5em} % for the horizontal padding
	{\renewcommand{\arraystretch}{1.2}% for the vertical padding
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
	Average Latency & 12.61 \\\hline
	Maximum Latency & 17.041 \\\hline
	Minimum Latency & 7.872 \\\hline
	Standard Deviation & 1.8 \\\hline
	\end{tabular}}
	\end{table}

@@

	After the QEMU configurations, Figure \ref{fig:max_latency_rt_kernelparam_host_qemu}

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/6rt_kernelparam_host_qemu/max_latency_rt_kernelparam_host_qemu/max_latency_rt_kernelparam_host_qemu.png}
		\caption[After QEMU configurations]{After QEMU configurations}
		\label{fig:max_latency_rt_kernelparam_host_qemu}
	\end{figure}

	\begin{table}[H]
		\centering
		\caption[Latency statistics of Salamander 4 after QEMU configurations]{Latency statistics of Salamander 4 virtualization after QEMU configurations in microseconds}
		\label{tab:latency_statistics_virt}
		\setlength{\tabcolsep}{0.5em} % for the horizontal padding
		{\renewcommand{\arraystretch}{1.2}% for the vertical padding
		\begin{tabular}{|c|c|}\hline
		\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
		Average Latency & 16.26 \\\hline
		Maximum Latency & 17.134 \\\hline
		Minimum Latency & 14.532 \\\hline
		Standard Deviation & 0.3 \\\hline
		\end{tabular}}
		\end{table}

@@

%
% Hier beginnt der Anhang.
%
\clearpage
\appendix
\begin{comment}
\chapter{Anhang A}
\clearpage
\chapter{Anhang B}
\end{comment}
